---
title: "Usage"
author: "Tianxiang Ren"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview
The source R code for _Svoleequation_ is as follows:

```{r eval=FALSE}
Solveequation <- function(f,a,b,eps=1e-5){
  if (f(a)*f(b)>0)
    list(fail="finding root is fail!")
  else{
    repeat {
      if (abs(b-a)<eps) break      
      x <- (a+b)/2
      if (f(a)*f(x)<0)
        b <- x
      else
        a <- x
    }
    list(root=(a+b)/2, fun=f((a+b)/2))
  }
}

```

The above code is a function to find the root of nonlinear equation by dichotomy, it involves 'ifelse', 'repeat', which are known to be slow.




The source R code for _norm.fun_ is as follows:

```{r eval=FALSE}
norm.fun <- function(theta,x) 
{	
  mu <- theta[1]
  sigma1 <- theta[2] 	
  n <- length(x)
  logL <- -0.5*n*log(2*pi)-0.5*n*log(sigma1)-(1/(2*sigma1))*sum((x-mu)**2) 
  return(-logL)  
}

```


The above code is a function to find the MLE of the mean and variance.




The source R code for _N.test_ is as follows:

```{r eval=FALSE}
N.test<- function(x,mu,sigma,a=0.05,alternative='two.side'){  
  xbar <- mean(x)
   n <- length(x)	 

if(alternative=='two.side') 
{
  N <- qnorm(a/2) 
  area1 <- xbar-(sigma/n)**0.5*N
  area2 <- xbar+(sigma/n)**0.5*N
  area=c(area1,area2)
  NT=(xbar-mu)/(sigma/n)**0.5 
  TF='reject' 
  if ( abs(NT)<abs(N))  
  {
    TF='accept'  
  }
  result=list('accept_or_reject'=TF,'interval estimation'=area)
  
}

if(alternative=='less')
{
  N=qnorm(a)
  area1=xbar+(sigma/n)**0.5*N
  area2=Inf  
  area=c(area1,area2)
  
  NT=(xbar-mu)/(sigma/n)**0.5
  TF='reject'
  if (NT>N)
  {
    TF='accept'
  }
  result=list('accept_or_reject'=TF,'interval estimation'=area)
  
}

if(alternative=='greater')
{
  N=-qnorm(a)   
  area1=-Inf
  area2=xbar-(sigma/n)**0.5*N
  
  area=c(area1,area2)
  
  NT=(xbar-mu)/(sigma/n)**0.5
  TF='reject'
  if (NT<N)
  {
    TF='accept'
  }
  result=list('accept_or_reject'=TF,'interval estimation'=area)
}

return(result)
}

```
The above code is a function to find the interval estimation and  hypothesis testing, it involves 'ifelse', 'list', which are known to be slow.





